---
title: "Weight of Fish"
author: "Aeilani Felix"
date: "Spring 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
We will find the best model by using two variables to predict the weight of the perch,then we will compare this to the model that is best overall.


## Perch

```{r}
Fish <- read.csv("Fish.csv")
perch <- filter(Fish, Species == "Perch")
```

```{r}
perch <- select(perch,-Species)
```

### Best Models
We find best models for all three species. 

### Best Two regressor model
```{r}
perchModel <- lm(Weight~., data=perch)
summary(perchModel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```

The best two parameters to predict weight is height and width.
```{r}
summary.out$which[3,]
```

```{r}
best2.model <- lm(Weight~Height+Width,data=perch)
summary(best2.model)
```

```{r}
anova(perchModel,best2.model)
```


## Pike
```{r}
pike = filter(Fish, Species == "Pike")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
#print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

### Best Two regressor model

```{r}
pikemodel=lm(Weight~Length1+Length3, data=pike)
summary(pikemodel)
```

The best two parameters to predict weight in a pike Fish is l1 and l3.


## Roach
```{r}
Roach = filter(Fish, Species == "Roach")
```
### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=Roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
#print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

the best two variables for roach and length3 and width.

### Best Two regressor model
```{r}
Roachmodel=lm(Weight~Length3+Width, data=Roach)
summary(Roachmodel)
```

The best model for the adjusted r squared is 0.8482.


## Final Summary Statements

Looking at data collected by all three models from lowest to highest. Roach being 0.8482 then perch at 0.94 and pike at 0.96.This is concluding that pike is the best model of the 3 since it was the highest value. 